MSA Asthma Place of Service Timeseries

### 2018-06-12 r_scripts/analysis/msa_asthma_timeseries.Rmd
updated standardized plot. Too much noise to put in the paper.

# plot of expected over observed
ggplot(data=exp_n, aes(x=week_date, y=diff_rate, 
    group = service_place, color = service_place)) +
  geom_point() +                 
  facet_wrap(~metroarea)
```

>>>>

# find mean and standard deviation for each difference rate by place of service
# and metroarea
normalize_val <- exp_n %>% 
  group_by(metroarea, service_place) %>% 
  summarise(mu_diff = mean(diff_rate), sd_diff = sd(diff_rate))

# join sd to diff and calcualte normalized difference
estimated_n <- exp_n %>% 
  left_join(normalize_val, by = c("metroarea", "service_place")) %>% 
  mutate(diff_rate_sd = (diff_rate - mu_diff)/sd_diff)

# plot of expected over observed
ggplot(data=estimated_n, aes(x=week_date, y=diff_rate_sd, 
    group = service_place, color = service_place)) +
  geom_point() +                 
  facet_wrap(~metroarea)
```
